The eclipse of the V773 Tau B circumbinary disk

### 2022-06-24 src/tex/ms.tex
tau_B orbit plots
AA styles
added bundle scripts

@@

\usepackage[nolist]{acronym}

\acrodef{vlba}[VLBA]{Very Long Baseline Array}

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\usepackage{nccmath}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}
% the three lines suppress the hyperref 'link empty' warnings
% explanation at: https://tex.stackexchange.com/questions/345764/journal-class-shows-package-hyperref-warning-suppressing-link-with-empty-targe
\makeatletter
\renewcommand*\aa@pageof{, page \thepage{} of \pageref*{LastPage}}

@@

\title{The eclipse of the V773 Tau B circumbinary disk}

@@

The bound components of V773 Tau were initially identified as A, B and C (see Figure~\ref{fig:cartoon}).
%
The A component was resolved by \ac{vlba} observations to be a binary system with $P_{AaAb}=51.1003\pm 0.0022$ days and an eccentricity of $e=0.2710\pm 0.0072$ \citep{Torres12}.
%
The A binary becomes more luminous in radio waves during the periastron passage of the A stars, which is thought to be from the interacting magnetic fields of the two stars \citep{Torres12}.

@@

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_b_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau AB system.
        %
        A is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
      \label{fig:v773orbitize}
 %     \script{analyze_and_plot_C_orbit_bundle.py}
\end{center}
\end{figure*}

@@

With the updated orbital bundles generated for the AB system, we then took the measured AC astrometry as reported in Table 1 of \citet{Duchene03} and Table 1 of \citet{Boden12} and combined it with the 2021 astrometry.
%
We then corrected the AC relative astrometry using the measured masses of A and B and calculated the distance from C to the the barycenter of AB (called C-AB).
%
Using the C-AB astrometry, we carried out an {\tt orbitize!} fit with parameters identical to that of the AB system.
%
The orbital period of C around the AB system is on the order of hundreds of years, and so only a short arc of the orbit is traced out across the observed epochs.
%
The resultant orbital bundle shows a much wider spread of orbital parameters, ranging from periods of several decades to almost a thousand years.
%
The orbital bundle includes the combined mass of AB and C, including some unphysically low masses, so we keep bundles with masses between 3.5 and 7.0 $M_\odot$.

@@

In this Section we consider the dynamics of a circumbinary disk in this quadrupole star system. 
%
In order for the stellar system to be stable, each binary must be inclined by less than about $40^\circ$ to the AB binary orbital plane otherwise, the stars will undergo Kozai-Lidov (KL) oscillations of eccentricity and inclination \citep{vonZeipel1910,Kozai1962,Lidov1962}.
%
A stable circumbinary disk around stars undergoing KL oscillations is unlikely. 
%
The disk, however, is likely to  be above the critical KL inclination since is it close to $90^\circ$ to the AB binary orbital plane \citep{Lubow2017,Zanazzi2017}.
%
If the disk were orbiting a single star, it would be KL unstable \citep{Martin2014,Fu2015} and would move towards alignment with the AB binary orbital plane on a timescale of tens of orbital periods of the AB binary.
%
However, the inner binary causes nodal precession that can stabilise the disk against KL oscillations \citep{Verrier2009,Martin2022} and lead to polar alignment in which the disk is perpendicular to the binary orbit and aligned to the eccentricity vector of the inner binary \citep{Martin17}.
%

>>>>

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\usepackage{nccmath}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}

@@

% the three lines suppress the hyperref 'link empty' warnings
% explanation at: https://tex.stackexchange.com/questions/345764/journal-class-shows-package-hyperref-warning-suppressing-link-with-empty-targe
\makeatletter
\renewcommand*\aa@pageof{, page \thepage{} of \pageref*{LastPage}}

@@

\title{The eclipse of the V773 Tau B circumbinary disk\thanks{The manuscript and processing scripts are available in a GitHub repository at \url{https://github.com/mkenworthy/V773TauBdisk}. Processed photometric data and light curves are available in electronic form at the CDS via anonymous ftp to \url{cdsarc.u-strasbg.fr} (130.79.128.5) or via \url{http://cdsweb.u-strasbg.fr/cgi-bin/qcat?J/A+A/}}}

@@

The bound components of V773 Tau were initially identified as A, B and C (see Figure~\ref{fig:cartoon}).
%
The A component was resolved by Very Long Baseline Array observations to be a binary system with $P_{AaAb}=51.1003\pm 0.0022$ days and an eccentricity of $e=0.2710\pm 0.0072$ \citep{Torres12}.
%
The A binary becomes more luminous in radio waves during the periastron passage of the A stars, which is thought to be from the interacting magnetic fields of the two stars \citep{Torres12}.

@@

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_b_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau AB system.
        %
        A is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
      \label{fig:v773orbitize}
      \script{analyze_and_plot_AB_orbit_bundle.py}
\end{center}
\end{figure*}

@@

With the updated orbital bundles generated for the AB system, we then took the measured AC astrometry as reported in Table 1 of \citet{Duchene03} and Table 1 of \citet{Boden12} and combined it with the 2021 astrometry.
%
We then corrected the AC relative astrometry using the measured masses of A and B and calculated the distance from C to the the barycentre of AB (called C-AB).
%
Using the C-AB astrometry, we carried out an {\tt orbitize!} fit with parameters identical to that of the AB system.
%
The orbital period of C around the AB system is on the order of hundreds of years, and so only a short arc of the orbit is traced out across the observed epochs.
%
The resultant orbital bundle shows a much wider spread of orbital parameters, ranging from periods of several decades to almost a thousand years.
%
The orbital bundle includes the combined mass of AB and C, including some unphysically low masses, so we keep bundles with masses between 3.5 and 7.0 $M_\odot$.

@@

In this Section we consider the dynamics of a circumbinary disk in this quadruple star system. 
%
In order for the stellar system to be stable, each binary must be inclined by less than about $40^\circ$ to the AB binary orbital plane otherwise, the stars will undergo Kozai-Lidov (KL) oscillations of eccentricity and inclination \citep{vonZeipel1910,Kozai1962,Lidov1962}.
%
A stable circumbinary disk around stars undergoing KL oscillations is unlikely. 
%
The disk, however, is likely to  be above the critical KL inclination since is it close to $90^\circ$ to the AB binary orbital plane \citep{Lubow2017,Zanazzi2017}.
%
If the disk were orbiting a single star, it would be KL unstable \citep{Martin2014,Fu2015} and would move towards alignment with the AB binary orbital plane on a timescale of tens of orbital periods of the AB binary.
%
However, the inner binary causes nodal precession that can stabilise the disk against KL oscillations \citep{Verrier2009,Martin2022} and lead to polar alignment in which the disk is perpendicular to the binary orbit and aligned to the eccentricity vector of the inner binary \citep{Martin17}.
%
